Declarative Deployment Reconfiguration of Pulverised Collective Adaptive Systems at Runtime \thanks{ This work has been supported by the Italian PRIN Project COMMON-WEARS (2020HCWWLP) and the EU/MUR FSE REACT-EU PON R\&I 2014-2020. }

### 2023-05-20 paper-2023-acsos-pulverization.tex
Update approach name

\newcommand{\ourframework}{\textsc{pulse-refrakt}}

@@

In this work,
we continue the research on pulverised systems by providing two key contributions:
\textbf{first}, we extend the theoretical framework of pulverisation by adding support for
\emph{runtime configuration rules}, allowing pulverised components to move at runtime across different hosts;
\textbf{second}, we provide a practical implementation in Kotlin called \ourframework{} which,
to the best of our knowledge,
is the first \emph{practical framework supporting pulverisation}. % for a general-purpose language.
%
To evaluate \ourframework{}, we exercise it through two case studies:
a small-scale real-wold demonstration, and a city-scale simulated scenario.

>>>>

\acrodef{ourframework}[\textsc{PulvReAKt}]{Pulverisation with Reconfigurable Adaption in Kotlin}
\newcommand{\ourframework}{\ac{ourframework}}

@@

In this work,
we continue the research on pulverised systems by providing two key contributions:
\textbf{first}, we extend the theoretical framework of pulverisation by adding support for
\emph{runtime configuration rules}, allowing pulverised components to move at runtime across different hosts;
\textbf{second}, we provide a practical implementation in Kotlin called \emph{\ourframework{}} which,
to the best of our knowledge,
is the first \emph{practical framework supporting pulverisation}. % for a general-purpose language.
%
To evaluate \ourframework{}, we exercise it through two case studies:
a small-scale real-wold demonstration, and a city-scale simulated scenario.
